Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
schematic diagram, a bit more details

II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2

II.4 generalises II.3, and offers a different proof for I.2.3

>>>>

II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.

II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .
